Magnetised Polish doughnuts revisited

### 2017-07-11 paper_revised_v2/paper_revised_v2.tex
breaking properly eq. B6 when using two-column format
final version

\begin{figure*}[t]
\centering
\includegraphics[scale=0.14]{figures/fig1a.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.14]{figures/fig1b.pdf}
\hspace{-0.2cm}
\includegraphics[scale=0.14]{figures/fig1c.pdf}
\caption{Comparison with Komissarov's solution for a constant angular momentum model. The left panel shows the rest-mass density distribution in logarithm scale for all radii and all angles while the middle and right panels show, respectively, the angular profile of the logarithm of the rest-mass density at the centre of the disc and the radial profile of the rest-mass density at the equatorial plane.}
\label{komissarov}
\end{figure*}

@@

We start by assessing our procedure by first building an extra disc model that can be directly compared with one of the two models in~\citet{Komissarov:2006}. This is shown in Figure~\ref{komissarov}, which corresponds to the same constant specific angular momentum model A presented by~\citet{Komissarov:2006}. The parameters of this model are $a=0.9$, $\beta_{\mathrm{m}_{\mathrm{c}}}=0.1$, and $l=2.8$.
The visual comparison shows that our approach can reproduce those previous results with good agreement. The rest-mass density distribution in the $(r\sin\theta,r\cos\theta)$ plane shown in the left panel of Fig.~\ref{komissarov} is remarkably similar to that shown in the left panel of Fig.~2 in~\citet{Komissarov:2006}. Not only the morphology of both models is nearly identical but also the range of variation of the rest-mass density and the location of the disc centre agree well in both cases. This can be most clearly seen in the middle and right panels of Fig.~\ref{komissarov} which show, repectively, the angular profile at $r_{\rm c}$ and the radial profile at $\theta=\pi/2$. These two figures can be directly compared with Fig.~3 of~\citet{Komissarov:2006}. It is relevant to mention that very small changes in the location of the inner radius $r_{\mathrm{in}}$ have a significant effect on the maximum value of the rest-mass density, which explains the small differences between our figures and the ones presented in~\citet{Komissarov:2006}.

@@

\left[\left(-\partial_r W \left(\frac{\lambda -1 }{\lambda}\right) \frac{1}{K+K_{\mathrm{m}}\mathcal{L}^{\lambda - 1}}\right) + \left(-\Delta W \left(\frac{\lambda -1}{\lambda}\right)\frac{-(\lambda - 1) K_{\mathrm{m}} \mathcal{L}^{\lambda - 2} \partial_r \mathcal{L}}{(K+K_{\mathrm{m}}\mathcal{L}^{\lambda - 1})^2}\right)\right]\,.

>>>>

\begin{figure*}[t]
\centering
\includegraphics[scale=0.14]{figures/fig1a.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.14]{figures/fig1b.pdf}
\hspace{-0.2cm}
\includegraphics[scale=0.14]{figures/fig1c.pdf}
\caption{Comparison with Komissarov's solution for a constant angular momentum model. The left panel shows the rest-mass density distribution in logarithm scale for all radii and all angles while the middle and right panels show, respectively, the angular profile of the logarithm of the rest-mass density at the centre of the disc and the radial profile of {\bf the logarithm of} the rest-mass density at the equatorial plane.}
\label{komissarov}
\end{figure*}

@@

We start by assessing our procedure by first building an extra disc model that can be directly compared with one of the two models in~\citet{Komissarov:2006}. This is shown in Figure~\ref{komissarov}, which corresponds to the same constant specific angular momentum model A presented by~\citet{Komissarov:2006}. The parameters of this model are $a=0.9$, $\beta_{\mathrm{m}_{\mathrm{c}}}=0.1$, and $l=2.8$.
The visual comparison shows that our approach can reproduce those previous results with good agreement. The rest-mass density distribution in the $(r\sin\theta,r\cos\theta)$ plane shown in the left panel of Fig.~\ref{komissarov} is remarkably similar to that shown in the left panel of Fig.~2 in~\citet{Komissarov:2006}. Not only the morphology of both models is nearly identical but also the range of variation of the rest-mass density and the location of the disc centre agree well in both cases. This can be most clearly seen in the middle and right panels of Fig.~\ref{komissarov} which show, repectively, the angular profile at $r_{\rm c}$ and the radial profile at $\theta=\pi/2$. {\bf The middle figure} can be directly compared with Fig.~3 of~\citet{Komissarov:2006}. It is relevant to mention that very small changes in the location of the inner radius $r_{\mathrm{in}}$ have a significant effect on the maximum value of the rest-mass density, which explains the small differences between our figures and the ones presented in~\citet{Komissarov:2006}.

@@

\left[\left(-\partial_r W \left(\frac{\lambda -1 }{\lambda}\right) \frac{1}{K+K_{\mathrm{m}}\mathcal{L}^{\lambda - 1}}\right) 
\right.
&+& \left. \left(-\Delta W \left(\frac{\lambda -1}{\lambda}\right)\frac{-(\lambda - 1) K_{\mathrm{m}} \mathcal{L}^{\lambda - 2} \partial_r \mathcal{L}}{(K+K_{\mathrm{m}}\mathcal{L}^{\lambda - 1})^2}\right)\right]\,.
